%\subsection{Commandline Interfaces}

In this section we describe syntax and behavior of the commands made available by the WMS-UI to allow job/DAG 
submission, monitoring and control. In the commands synopsis the mandatory arguments are showed between 
angle brackets $<$arg$>$) whilst the optional ones between square brackets ([arg]).

Commands for accessing the WMS through the WMProxy service are described in document ~\cite{WMPROXY}.
Note that usage of the WMProxy submission and control client commands is strongly recommended as they 
provide full support for all new functionality and enhancements of the WMS. 

Before going to the single commands let's have a look at how the WMS-UI can be configured.


\medskip
\subsubsection{Commands Configuration}
\label{config}

\textbf{VO-Specific}

Configuration of the WMS User Interface VO-specific parameters is accomplished through the file:

\smallskip
\begin{verbatim}
$GLITE_LOCATION/etc/<vo name>/glite_wmsui.conf 
\end{verbatim}
\smallskip


i.e. there is one directory and file for each supported VO. 

The common WMS-UI configuration rpm (\textit{glite-wms-ui-configuration}) installs the following example file:

\smallskip
\begin{verbatim}
$GLITE_LOCATION/etc/vo_template/glite_wmsui.conf
\end{verbatim}
\smallskip

If the configuration for your VO is not present on the WMS-UI machine you must create in \$GLITE\_LOCATION/etc a 
directory, named as the VO (lower-case), copy in it the above mentioned template file and update it opportunely.

The \emph{glite\_wmsui.conf} file is a classad containing the following fields:

\smallskip

\begin{itemize}
 \item \textbf{VirtualOrganisation} this is a string representing the name of the virtual organisation the file refers to.
   It should match with the name of the directory containing the file (i.e. the VO). This parameter is 
   mandatory. 
 \item \textbf{NSAddresses} this is a list of strings representing the addresses ($<$hostname$>$:$<$port$>$) of the Network 
   Servers available for the given VO. Job submission is performed towards the NS picked-up randomly from 
   the list and in case of failure it is retried on each other listed NS until succes or the end of the 
   list is reached. This parameter is mandatory.
 \item \textbf{LBAddresses} this is a list of strings or a list of lists of strings representing the address or list 
   of addresses ($<$hostname$>$:$<$port$>$) of the LB servers available for the given VO for the corresponding NS. 
   I.e. the first list of LB addresses correspond to the first NS in the NSAddresses list, the second list 
   of LB addresses correspond to the second NS in the NSAddresses list and so on.
   When job submission is performed, the WMS-UI after having chosen the NS, choses randomly one LB server within
   the corresponding list and uses it for generating the job identifier so that all information related with 
   that job will be managed by the chosen LB server. This allows distributing load on several LB servers.  
   This parameter is mandatory.
 \item \textbf{HLRLocation} this is a string representing the address ($<$hostname$>$:$<$port$>$:$<$X509contact string$>$)  of the 
   HLR for the given VO. HLR is the service responsible for managing the economic transactions and the 
   accounts of user and resources. This parameter is not mandatory. It is not present in the file by default.
   If present, it makes the WMS-UI automatically add to the job description the HLRLocation JDL attribute 
   (if not specified by the user) and this enables accounting.
 \item \textbf{MyProxyServer} this is a string representing the MYProxy server address ($<$hostname$>$) for the given VO. 
   This parameter is not mandatory. It is not present in the file by default. If present, it makes the WMS-UI 
   automatically add to the job description the MyProxyServer JDL attribute (if not specified by the user) 
   and this enables proxy renewal. If the myproxy client package is installed on the WMS-UI node, then this 
   parameter should be set equal to the MYPROXY\_SERVER environment variable.
 \item \textbf{LoggingDestination} this is a string defining the address ($<$host$>$:$[<$port$>]$;) of the LB logging service 
   (glite-lb-locallogger logging daemon ) to be targeted when logging events. The WMS-UI first checks the 
   environment for the EDG\_WL\_LOG\_DESTINATION variable and only if this is not set, the value of the 
   LoggingDestination parameter is taken into account. Otherwise the job related events are logged to the 
   LB logging service running on the WMS node.

\end{itemize}
\smallskip

Here below is provided an example of configuration file for the "atlas" Virtual Organisation. 
This implies that the file path has to be \textit{\$GLITE\_LOCATION/etc/atlas/glite\_wmsui.conf}. 

\smallskip
\begin{verbatim}

[
 VirtualOrganisation = "atlas";
 NSAddresses = {
   "ibm139.cnaf.infn.it:7772",
   "gundam.cnaf.infn.it:7772"
   };
 LBAddresses = {
   {"ibm139.cnaf.infn.it:9000"},
   {"gundam.cnaf.infn.it:9000", "neo.datamat.it:9000", "grid003.ct.infn.it:9876"}
  };
 HLRLocation = "lilith.to.infn.it:56568:/C=IT/O=INFN/OU=Personal Certificate/L=Torino/CN=Andrea 
                Guarise/Email=A.Guarise@to.infn.it";
 MyProxyServer = "skurut.cesnet.cz";
 LoggingDestination = "localhost:9002";  // local instance of LB logging service
]

\end{verbatim}
\medskip
\medskip


\textbf{Generic}


Configuration of the WMS User Interface generic parameters is accomplished through the file:

\smallskip
\begin{verbatim}
$GLITE_LOCATION/etc/glite_wmsui_cmd_var.conf
\end{verbatim}
\smallskip


Update the content of the latter file according to your needs.

The \textit{glite\_wmsui\_cmd\_var.conf} file is a classad containing the following fields:


\smallskip

\begin{itemize}
 \item \textbf{requirements} this is an expression representing the default value for the requirements expression 
   in the JDL job description. This parameter is mandatory. The value of this parameter is assigned by 
   the WMS-UI to the requirements attribute in the JDL if not specified by the user. If the user has instead 
   provided an expression for the requirements attribute in the JDL, the one specified in the configuration 
   file is added (in AND) to the existing one. 
   E.g. if in the glite\_wmsui\_cmd\_var.conf configuration file there is: 

   \begin{scriptsize}   
   \textit{requirements = other.GlueCEStateStatus == "Production" ;} 
   \end{scriptsize}

   and in the JDL file the user has specified: 

   \begin{scriptsize}   
   \textit{requirements = other.GlueCEInfoLRMSType == "PBS";} 
   \end{scriptsize}

   then the job description that is passed to the WMS contains 

   \begin{scriptsize}   
   \textit{requirements = (other.GlueCEInfoLRMSType == "PBS") \&\& (other.GlueCEStateStatus == "Production");} 
   \end{scriptsize}
      
   Obviously the setting TRUE for the requirements in the configuration file does not have any impact on the evaluation 
   of job requirements as it would result in: 

   \begin{scriptsize}   
   \textit{requirements = (other.GlueCEInfoLRMSType == "PBS") \&\& TRUE ;}
   \end{scriptsize}

 \item \textbf{rank} this is an expression representing the default value for the rank expression in the JDL job 
   description. The value of this parameter is assigned by the WMS-UI to the rank attribute in the JDL if not 
   specified by the user. This parameter is mandatory.   
 \item \textbf{RetryCount} this is an integer representing the default value for the number of submission retries for 
   a job upon failure due to some grid component (i.e. not to the job itself). The value of this parameter 
   is assigned by the WMS-UI to the RetryCount attribute in the JDL if not specified by the user.   
 \item \textbf{DefaultVo} this is a string representing the name of the virtual organisation to be taken as the user s 
   VO (VirtualOrganisation attribute in he JDL) if not specified by the user neither in the credentials 
   VOMS extension, nor directly in the job description nor through the --vo option. This attribute can be 
   either set to  unspecified  or not included at all in the file to mean that no default is set for the VO. 
 \item \textbf{ErrorStorage} this is a string representing the path of the directory where the WMS-UI creates log files. 
   This directory is not created by the WMS-UI, so It has to be an already existing directory. Default for this 
   parameter is /tmp.   
 \item \textbf{OutputStorage} this is a string defining the path of the directory where the job OutputSandbox files are 
   stored if not specified by the user through commands options. This directory is not created by the WMS-UI, 
   so It has to be an already existing directory. Default for this parameter is /tmp. 
 \item \textbf{ListenerStorage} this is a string defining the path of the directory where are created the pipes where 
   the glite\_wms\_console\_shadow process saves the job standard streams for interactive jobs. Default for 
   this parameter is /tmp.   
 \item \textbf{LoggingTimeout} this is an integer representing the timeout in seconds for asynchronous logging function 
   called by the WMS-UI when logging events to the LB. Recommended value for WMS-UI that are non-local to the 
   logging service (glite-lb-logd logging daemon) is not less than 30 seconds. 
 \item \textbf{LoggingSyncTimeout} this is an integer representing the timeout in seconds for synchronous logging function
   called by the WMS-UI when logging events to the LB. Recommended value is not less than 30 seconds.   
 \item \textbf{DefaulStatusLevel} this is an integer defining the default level of verbosity for the glite-job-status 
   command. Possible values are 0,1,2 and 3. 1 is the default.
 \item \textbf{DefaultLogInfoLevel} this is an integer defining the default level of verbosity for the glite-job-logging-info
   command. Possible values are 0,1,2 and 3. 1 is the default. 
   Default for this parameter is 0.   
 \item \textbf{NSLoggerLevel} this is an integer defining the quantity of information logged by the NS client. Possible 
   values range from 0 to 6. 0 is the defaults and means that no information is logged. Default for this 
   parameter is 0. 

\end{itemize}
\smallskip


Hereafter is provided an example of the \textit{\$GLITE\_LOCATION/etc/glite\_wmsui\_cmd\_var.conf} configuration file: 


\smallskip
\begin{verbatim}

[ 
 requirements = other.GlueCEStateStatus == "Production" ; 
 rank = - other.GlueCEStateEstimatedResponseTime ; 
 RetryCount = 3 ; 
 ErrorStorage= "/var/tmp" ; 
 OutputStorage="/tmp/jobOutput"; 
 ListenerStorage = "/tmp" 
 LoggingTimeout = 30 ; 
 LoggingSyncTimeout = 45 ;  
 DefaultStatusLevel = 1 ; 
 DefaultLogInfoLevel = 0; 
 NSLoggerLevel = 2; 
 DefaultVo = "EGEE"; 
] 

\end{verbatim}
\smallskip

The files: 

\smallskip
\begin{verbatim}
$GLITE_LOCATION/etc/glite_wmsui_cmd_err.conf
\end{verbatim}
\smallskip

and 

\smallskip
\begin{verbatim}
$GLITE_LOCATION/etc/glite_wmsui_cmd_help.conf 
\end{verbatim}
\smallskip

contain respectively the error codes and error messages returned by the WMS-UI and the text describing the 
commands usage.

\newpage
\subsubsection{Common behaviours}
\label{commonbeh}

As mentioned in the previous section~\ref{quickstart}, 
\textit{\$GLITE\_LOCATION/etc} is the WMS-UI configuration area: it includes the file specifying 
the mapping between error codes and error messages (glite\_wmsui\_cmd\_err.conf), 
the file containing the detailed description of each command (glite\_wmsui\_cmd\_help.conf) and the 
actual configuration files: glite\_wmsui\_cmd\_var.conf and $<$VO name$>$/glite\_wmsui.conf). 
The latter files are the only ones that could need to be edited and tailored according to the user/platform 
characteristics and needs. 
The \emph{glite\_wmsui\_cmd\_var.conf } file contains the following information that are read by and have 
influence on commands behaviour: 

\begin{itemize}
\item default location of the local storage areas for the Output sandbox files,
\item default location for the WMS-UI log files,
\item default values for the JDL mandatory attributes,
\item default values for timeouts when logging events to the LB,
\item default logging destination,
\item user's default VO,
\item default level of information displayed by the monitoring commands
\end{itemize}

Inside \textit{\$GLITE\_LOCATION/etc} there is instead a directory for each supported Virtual Organisation and 
named as the VO lower case e.g. for atlas we will have \$GLITE\_LOCATION/etc/atlas/) that contains a vo-specific 
configuration file glite\_wmsui.conf specifying the list of Network Servers and LBs accessible for the given VO.

When started, WMS-UI commands search for the configuration files in the following locations, in order of 
precedence:
 
\begin{itemize}
 \item \$GLITE\_WMS\_LOCATION/etc,
 \item \$GLITE\_LOCATION/etc,  
 \item /opt/glite/etc,
 \item /usr/local/etc,
 \item /etc
\end{itemize}

If none of the locations contains needed files an error is returned to the user.

Since several users on the same machine can use a single installation of the WMS-UI, people concurrently issuing 
WMS-UI commands share the same configuration files. Anyway for users (or groups of users) having particular needs 
it is possible to use "customised" WMS-UI configuration files through the --config and -config-vo options supported 
by each WMS-UI command.

Indeed every command launched specifying \emph{--config file\_path} reads its configuration settings in the file 
pointed by "file\_path" instead of the default configuration file. The same happens for the vo-specific 
configuration file if the command is started using specifying  \emph{-config-vo vo\_file\_path}. 
Hence the user only needs to create such file according to her needs and to use the appropriate options to work 
under "private" settings.

Moreover if the user wants to make this change in some way permanent avoiding the use for each issued command 
of the --config option, she can set the environment variable GLITE\_WMSUI\_CONFIG\_VAR to point to the non-standard 
path of the configuration file. Indeed if that variable is set commands will read settings from file 
"\$GLITE\_WMSUI\_CONFIG\_VAR". Anyway the --config option takes precedence on all other settings.

Exactly the same applies for the GLITE\_WMSUI\_CONFIG\_VO environment variable and the --config-vo option.

It is important to note that since the job identifiers implicitly holds the information about the LB that is 
managing the corresponding job, all the commands taking the job Id as input parameter do not take into account 
the LB addresses listed in the configuration file to perform the requested operation also if the -config-vo option 
has been specified.

Hereafter are listed the options that are common to all WMS-UI commands: 

{\begin{verbatim}
--config file_path
--config-vo file_path
--noint
--debug
--logfile file_path
--version
--help
\end{verbatim} 

The \verb!--noint! option skips all interactive questions to the user and goes ahead in the command execution. 
All warning messages and errors (if any) are written to the file 

\textbf{$<$command\_name$>$\-\_$<$UID$>$\-\_$<$PID$>$\-\_$<$date\_time$>$.log} 

in the location specified in the configuration file instead of the standard output. 
It is important to note that when \verb!--noint! is specified some checks on "dangerous actions" are skipped. 
For example if jobs cancellation is requested with this option, this action will be performed without requiring 
any confirmation to the user. The same applies if the command output will overwrite an existing file, so it is 
recommended to use the \verb!--noint! option in a safe context.

\medskip

The \verb!--debug! option is mainly thought for testing and debugging purposes; indeed it makes the commands 
print additional information while running. Every time an external API function call is encountered during the 
command execution, values of parameters passed to the API are printed to the user. The info messages are displayed 
on the standard output and are also written together with possible errors and warnings, to 

\textit{$<$command\_name$>$\-\_$<$UID$>$\-\_$<$PID$>$\-\_$<$date\-\_time$>$.log}.

\medskip

If \verb!--noint! option is specified together with \verb!--debug! option the debug message will not be printed on 
standard output.

\medskip

The \verb!--logfile! $<$file\_path$>$ option allows re-location of the commands log files in the location pointed 
by file\_path.

\medskip

The \verb!--version! and \verb!--help! options respectively make the commands display the WMS-UI current version and 
the command usage.

\medskip

Two further options that are common to almost all commands are \verb!--input! and \verb!--output!. The latter one 
makes the commands redirect the outcome to the file specified as option argument whilst the former reads a list of 
input items from the file given as option argument. The only exception is the glite\--job\--list\--match command 
that does not have the \verb!--input! option.

\medskip
\textbf{--input option}
\medskip
\smallskip
for all commands, the file given as argument to the \verb!--input! option shall contain a list of job identifiers 
in the following format: one \textit{jobId} for each line, comments beginning with a "\#" or a "*" character.  
If the input file contains only one \textit{jobId} (see the description of glite-job-submit command later in this 
document for details about \textit{jobId} format), then the request is directly submitted taking the 
\textit{jobId} as input, otherwise a menu is displayed to the user listing all the contained items, 
i.e. something like:

\smallskip
\begin{scriptsize}
\begin{verbatim}
---------------------------------------------------------------
1 : https://ibm139.cnaf.infn.it:9000/ZU9yOC7AP7AOEhMAHirG3w
2 : https://ibm139.cnaf.infn.it:9000/ZU9yOC767gJOEhMAHirG3w
3 : https://ibm135.cnaf.infn.it:9000/ZU9yOC7AP7A55TREAHirG3w
4 : https://grid012f.cnaf.infn.it:7846/ZUHY6707AP7AOEhMAHirG3w
5 : https://grid012f.cnaf.infn.it:9000/Cde341P7AOEhMAHirG3w
6 : https://ibm139.cnaf.infn.it:9000/BgT8T6H\_L92FsKq3OeTWOw
7 : https://ibm139.cnaf.infn.it:9000/lYlPBQez7fiXx9qq7BEdyw
8 : https://ibm139.cnaf.infn.it:9000/_f0Bm\_s6UdFPZIEjSglipg
a : all
q : quit
---------------------------------------------------------------
Choose one or more jobId(s) in the list - [1-10]all:
\end{verbatim} 
\end{scriptsize}
\smallskip

The user can choose one or more jobs from the list entering the corresponding numbers. Single jobs can be selected 
specifying the numbers associated to the job identifiers separated by commas. Ranges can also be selected 
specifying ends separated by a dash and it is worth mentioning that it is possible to select at the same time 
ranges and single jobs. E.g.:

\begin{itemize}
\item [2:] 	makes the command take the second listed \textit{jobId} as input
\item [1,4:]	makes the command take the first and the fourth listed \textit{jobId}s as input
\item [2-5:]	makes the command take listed \textit{jobId}s from 2 to 5 ends included) as input
\item [1,3-5,8:] selects the first job id in the list, the ids from the third to the fifth ends included) 
and finally the eighth one.
\item [all:]	makes the command take all listed \textit{jobId}s as input
\item [q:]	makes the command quit
\end{itemize}

Default value for the choice is all. 

If the \verb!--input! option is used together with the  \verb!--noint! then all \textit{jobId}s contained in 
the input file are taken into account by the command.

There are some commands whose \verb!--input! behaviour differs from the one just described. One of them is 
glite-job-submit: the input file contains in this case CEIds instead of \textit{jobId}s. 
As only one CE at a time can be the target of a submission, the user is allowed to choose one and only one CEId.
Default value for the choice is "1", i.e. the first CEId in the list. 
This is also the choice automatically made by the command when the \verb!--input! option is used together with 
the \verb!--noint! one.

The other commands are \textbf{glite-job-attach} and \textbf{glite-job-get-chkpt} whose \verb!--input! option 
allows to select one (just one) of the \textit{jobId}s contained in the input file.

\newpage

\input{glite-job-submit}
\newpage

\input{glite-job-list-match}
\newpage

\input{glite-job-cancel}
\newpage

\input{glite-job-output}
\newpage

\input{glite-job-attach}
\newpage

\input{glite-job-get-chkpt}
\newpage

\input{glite-job-status}
\newpage

\input{glite-job-logging-info}
\newpage


