\documentclass{egee}
\usepackage{doxygen}
\usepackage{tabularx}


\title{EGEE User's Guide}
\Subtitle{WMS Service}
\author{Fabrizio Pacini}
\DocIdentifier{EGEE-JRA1-TEC-572489}
\Date{\today}
\Activity{JRA1: Middleware Engineering and Integration}
\DocStatus{}
\Dissemination{PUBLIC}
\DocumentLink{https://edms.cern.ch/document/572489/1}

\Abstract{
This user's guide explains how to use Services offered by the gLite Workload Management System and 
the Logging and Bookkeeping Service. Commands and API for job submission and control described in 
this document allow accessing the WMS through the legacy interface, the Network Server. 
Commands and API for accessing the WMS through the Web-Service interface (WMProxy) and exploit all new 
WMS features (e.g. bulk submission, shared sandboxes, job's files perusal etc.) are described at 
https://edms.cern.ch/document/674643/1. 
Described features are fully supported by the WMS included in gLite version 3.0.0 or later.
}

\begin{document}

\input{frontmatter}

\newpage

\tableofcontents

\newpage

\section{Introduction}

The purpose of the Workload Manager Service (WMS) is to accept requests for job submission and management 
coming from its clients and take the appropriate actions to satisfy them.
The complexity of the management of applications and resources in the grid is hidden by the WMS to 
the users. Their interaction with the WMS is indeed limited to the description of the characteristics and 
requirements of the request via a high-level, user-oriented specification language, the Job Description 
Language (JDL) ~\cite{jdl-lang} and to the submission of it through the provided interfaces.

It is then responsibility of the WMS to translate these abstract resource requirements into a set of actual 
resources, taken from the overall grid resource pool, to which the user has access permission.
The JDL allows the description of the following request types supported by the WMS:
\begin{itemize}
   \item{Job: a simple application}
   \item{DAG: a direct acyclic graph of dependent jobs }
   \item{Collection: a set of independent jobs }
\end{itemize}

Jobs in turn can be batch, interactive, MPI-based, checkpointable, partitionable and parametric.
Support for job collections and parametric jobs is only available when the submission to the WMS 
is done through the WMProxy service whose features are described in document ~\cite{WMPROXY}.
Besides request submission, the WMS  also exposes additional functionality for request 
management and control such as cancellation, output retrieval and job files perusal. 
Request status follow-up can be instead achieved through the functionality exposed by the 
LB service ~\cite{lb}.

If a user belonging to a Virtual Organization wants to submit a job to the Grid, he/she must, first 
of all, describe it with an appropriate JDL file. The user is allowed to use whatever attribute for the 
description of a request without incurring in errors. 
Anyway only a certain set of attributes (the "supported" attributes) are taken into account by the WMS 
components for scheduling and submit the corresponding request. The "supported" attributes, their meaning 
and the way to use them to describe a job/DAG are described in detail in document ~\cite{jdl}.


\subsection{Service Architecture}
\label{arch}
\input{arch}


\subsection{Interactions with other Services}
\label{interactions}
\input{interactions}

\subsection {Security} 
\label{security}
\input{security}
 
\section{Quick-start Guide}
\label{quickstart}
\input{quickstart}

\newpage
\section{Reference Guide}
\label{refguide}

%The reference guide should contain detailed descriptions of all
%provided CLIs and APIs. There should be two subsections for those.

\subsection{Command-Line Interfaces}
\label{cli}
\input{cli2}


\newpage

\subsection{WMS client API Description}

The WMS client API supplies the client applications with a set of interfaces over the job description, 
submission, monitoring and control services made available by the gLite WMS.
The API provided methods could be conceptually grouped into two main categories that are Job Description and 
Job Submission, Monitoring \& Control. 
The Job Description functions provide the API customers with services to build consistent and syntactically 
correct job and jobs workflows (DAGs) descriptions in the JDL language. 
The Job Submission, Monitoring and Control methods handle instead:

\begin{itemize}
 \item Job submission for execution on a remote Computing Element, also encompassing: 
 \begin{itemize}                   
    \item Automatic resource discovery and selection
    \item Staging of the application input sandbox
    \item Restart of the job from a previously saved checkpoint state
    \item Job Partitioning
    \item Interactive communication with the running job
    \item Management of job workflows
 \end{itemize}
 \item Listing of resources suitable to run a specific job according to job requirements,
 \item Cancellation of one or more submitted jobs,
 \item Retrieval of the output files of one or more completed job.
 \item Retrieval of job bookkeeping and logging information.
 \item Retrieval of information from the proxy credentials needed by the user applications to interact 
       with the service.
\end{itemize}

A simple API for the management of job identifiers is also provided.
The main classes of the WMS client API (C$++$ and Java bindings are provided) are listed here below:
	       
\begin{itemize}
    \item \textbf{JobId}             		(job identifier representation)
    \item \textbf{Ad}, \textbf{JobAd}           (job description)
    \item \textbf{DAGAd}, \textbf{ExpDagAd}     (DAG description)
    \item \textbf{Job}                          (job submission, monitoring and control - all job types)
    \item \textbf{Request}                      (DAG and normal job submission, monitoring and control)
    \item \textbf{JobCollection}                (management of group of independent jobs)
    \item \textbf{UserJobs}                     (monitoring and control of all jobs owned by a user)
    \item \textbf{UserCredentials}              (user credentials information) 
\end{itemize}

\newpage

This is a simple usage example of the above listed classes for submitting a normal job:

\begin{scriptsize}
\begin{verbatim}
        ...
        // declare a job description object 
        glite::wms::jdl::JobAd jdl; 	
        // create the description object from a jdl file. Correctness of the description is checked 
        jdl.fromFile ( "/home/test/myjob.jdl" ) ; 
        // create a Request object from the job description. Request handles DAGs and normal jobs.
        // the Job class can instead be used for specific job types (e.g. Interactive, MPI etc.)
        glite::wmsui::api::Request   job(jdl);	
        // submit the job to the specified WMS (NShost, NSport) and store job information to the 
        // specified LB (LBhost , LBport).   
        glite::wmsutils::jobid::JobId jobid = job.submit ( NShost , NSPort , LBhost , LBport ) ;
        // print out the assigned job identifier 
        cout << "Success. The job identifier is: " << jobid.toString() << endl ;
        ...
\end{verbatim}
\end{scriptsize}
\smallskip


Detailed documentation of the above mentioned APIs is provided in the following section (~\ref{jscpp},~\ref{jdlcpp} 
and ~\ref{jobidcpp}). The documentation in HTML format for the C$++$ and Java bindings of the described 
APIs is available at the following URL \url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/glite-wms-api-index.shtml}. 
Usage examples and build hints for the C$++$ and the Java APIs are respectively available at: \\
\url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/ui_cpp_api_usage.shtml} and \\ 
\url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/ui_java_api_usage.shtml}. \\
The Java API documentation and the coding examples are available on-line and have not been included in this 
user's guide to not make this document size explode and to ease quick updates when needed.  

Note that the documentation describing the WMProxy Client API providing C++, Java and Python bindings
(also including the support for bulk submission and shared sandboxes) can be found at 
\url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/glite-wmproxy-api-index.shtml}.
Pointers to usage examples are provided in the above mentioned web page.
Usage of the WMProxy submission and control API is strongly recommended as it provides full            
support for all new functionality and enhancements of the WMS.


The WMS client software also includes the Brokerinfo Access API.
This API  consists of a simple class for parsing the \textit{.BrokerInfo} file ~\cite{brokerinfo}, which is a file 
generated by the Resource Broker during the match making phase on the basis of the data requirements 
(\textit{InputData} attribute) specified in the JDL and is copied on the CE worker node where the job is run. 
The \textit{.BrokerInfo} file contains information about the physical file names the job has to consider at run time, 
the protocols it can use to access those files and the Storage Elements that are close to the CE where the job is run.  
The Brokerinfo Access API is described in section ~\ref{brki}. HTML documentation is available at: \\
\url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/api_doc/brokerinfo-access/index.html}. 

\newpage
\subsection{Job Submission API---C++ binding}
\label{jscpp}
{
\renewenvironment{CompactList}{\itemize\itemsep -2pt}{\enditemize}
\def\section#1{}
\renewcommand{\contentsline}[4]{{\bf #2}\leaders\hbox{.}\hfill #3}
The documentation of C$++$ Job Submission API presented in this section was generated automatically from the 
comments in the API header files by Doxygen. The packages providing the Job Submission API are 
{\verb!org.glite.wms-ui.api-cpp!} and {\verb!org.glite.wms-ui.api-java!}.

The class hierarchy is depicted in the following list.
\input{hierarchy_js}
}

\noindent The Job Submission API classes are described in the
following sections.
{
\input{doxyhack}
\let\ddescription=\description
\let\denddescription=\enddescription
\renewenvironment{description}{\list{}{\labelwidth 4cm\leftmargin 4cm}}{\endlist}
% documentation for particular classes

\input{structglite_1_1wmsui_1_1api_1_1CollectionResult}
\include{classglite_1_1wmsui_1_1api_1_1Job}
\include{classglite_1_1wmsui_1_1api_1_1JobCollection}
\include{classglite_1_1wmsui_1_1api_1_1JobCollectionException}
\include{classglite_1_1wmsui_1_1api_1_1JobCollectNoJobException}
\include{classglite_1_1wmsui_1_1api_1_1JobException}
\include{classglite_1_1wmsui_1_1api_1_1JobOperationException}
\include{classglite_1_1wmsui_1_1api_1_1JobTimeoutException}
\include{classglite_1_1wmsui_1_1api_1_1Listener}
\include{classglite_1_1wmsui_1_1api_1_1Logging}
\include{classglite_1_1wmsui_1_1api_1_1paramStruct}
\include{classglite_1_1wmsui_1_1api_1_1Request}
\include{classglite_1_1wmsui_1_1api_1_1resultStruct}
\include{classglite_1_1wmsui_1_1api_1_1Shadow}
\include{classglite_1_1wmsui_1_1api_1_1ThreadException}
\include{classglite_1_1wmsui_1_1api_1_1UserCredential}
\include{classglite_1_1wmsui_1_1api_1_1UserJobs}

}



\subsection{Job Description API---C++ binding}
\label{jdlcpp}
{
\renewenvironment{CompactList}{\itemize\itemsep -2pt}{\enditemize}
\def\section#1{}
\renewcommand{\contentsline}[4]{{\bf #2}\leaders\hbox{.}\hfill #3}
The documentation of C$++$ Job Description API (also referred to as JDL API) presented in this section was 
generated automatically from the comments in the API header files by Doxygen.
The packages providing the Job Description API are {\verb!org.glite.wms.jdl!} and {\verb!org.glite.wms.jdlj!}.


The class hierarchy is depicted in the following list.
\input{hierarchy_jdl}
}

\noindent The Job Description API classes are described in the
following sections.
{
\input{doxyhack}
\let\ddescription=\description
\let\denddescription=\enddescription
\renewenvironment{description}{\list{}{\labelwidth 4cm\leftmargin 4cm}}{\endlist}
% documentation for particular classes

\input{classglite_1_1wms_1_1jdl_1_1Ad}
\include{classglite_1_1wms_1_1jdl_1_1AdAttributeException}
\include{classglite_1_1wms_1_1jdl_1_1AdClassAdException}
\include{classglite_1_1wms_1_1jdl_1_1AdConverter}
\include{classglite_1_1wms_1_1jdl_1_1AdEmptyException}
\include{classglite_1_1wms_1_1jdl_1_1AdFormatException}
\include{classglite_1_1wms_1_1jdl_1_1AdListException}
\include{classglite_1_1wms_1_1jdl_1_1AdMismatchException}
\include{classglite_1_1wms_1_1jdl_1_1AdSemanticException}
\include{classglite_1_1wms_1_1jdl_1_1AdSemanticGroupException}
\include{classglite_1_1wms_1_1jdl_1_1AdSemanticMandatoryException}
\include{classglite_1_1wms_1_1jdl_1_1AdSemanticPathException}
\include{classglite_1_1wms_1_1jdl_1_1AdSyntaxException}
\include{classglite_1_1wms_1_1jdl_1_1CannotGetAttribute}
\include{classglite_1_1wms_1_1jdl_1_1CannotRemoveAttribute}
\include{classglite_1_1wms_1_1jdl_1_1CannotSetAttribute}
\include{classglite_1_1wms_1_1jdl_1_1DAGAd}
\include{structglite_1_1wms_1_1jdl_1_1DAGAd_1_1Attributes}
\include{structglite_1_1wms_1_1jdl_1_1DAGAdDependencyIterator}
\include{classglite_1_1wms_1_1jdl_1_1DAGAdNodeIterator}
\include{classglite_1_1wms_1_1jdl_1_1DAGNodeInfo}
\include{classglite_1_1wms_1_1jdl_1_1ExpDagAd}
\include{structglite_1_1wms_1_1jdl_1_1InvalidDAG}
\include{structglite_1_1wms_1_1jdl_1_1InvalidNodeInfo}
\include{classglite_1_1wms_1_1jdl_1_1JdlAttributeList}
\include{classglite_1_1wms_1_1jdl_1_1JobAd}
\include{classglite_1_1wms_1_1jdl_1_1JobAdSchema}
\include{structglite_1_1wms_1_1jdl_1_1JobIdStruct}
\include{classglite_1_1wms_1_1jdl_1_1ManipulationException}
\include{classglite_1_1wms_1_1jdl_1_1NodeAd}
\include{structglite_1_1wms_1_1jdl_1_1NodeStruct}
\include{classglite_1_1wms_1_1jdl_1_1RequestAdException}

}

\subsection{Job Identifier API---C++ binding}
\label{jobidcpp}
{
\renewenvironment{CompactList}{\itemize\itemsep -2pt}{\enditemize}
\def\section#1{}
\renewcommand{\contentsline}[4]{{\bf #2}\leaders\hbox{.}\hfill #3}
The documentation of C$++$ Job Identifier API presented in this section was
generated automatically from the comments in the API header files by Doxygen.
The package providing the Job Identifier API is {\verb!org.glite.wms-utils.jobid!} for C$++$. The Java API is included
in package {\verb!org.glite.wms-ui.api-java!}

The class hierarchy is depicted in the following list.
\input{hierarchy_jobid}
}

\noindent The Job Identifier API classes are described in the
following sections. 
{
\input{doxyhack}
\let\ddescription=\description
\let\denddescription=\enddescription
\renewenvironment{description}{\list{}{\labelwidth 4cm\leftmargin 4cm}}{\endlist}
% documentation for particular classes

\input{classglite_1_1wmsutils_1_1jobid_1_1EmptyIdException}
\include{classglite_1_1wmsutils_1_1jobid_1_1JobId}
\include{classglite_1_1wmsutils_1_1jobid_1_1JobIdException}
\include{classglite_1_1wmsutils_1_1jobid_1_1WrongIdException}

}


\subsection{BrokerInfo Access API---C++ binding}
\label{brki}
{
\renewenvironment{CompactList}{\itemize\itemsep -2pt}{\enditemize}
\def\section#1{}
\renewcommand{\contentsline}[4]{{\bf #2}\leaders\hbox{.}\hfill #3}
The documentation of C$++$ BrokerInfo Access API presented in this section was generated automatically from the
comments in the API header files by Doxygen. The package providing the BrokerInfo Access API is 
{\verb!org.glite.wms.brokerinfo-access!}.

The class hierarchy is depicted in the following list.
\input{annotated_br}
}

\noindent The BrokerInfo Access API classes are described in the
following sections.
{
\input{doxyhack}
\let\ddescription=\description
\let\denddescription=\enddescription
\renewenvironment{description}{\list{}{\labelwidth 4cm\leftmargin 4cm}}{\endlist}
% documentation for particular classes

\input{classBrokerInfo}
\include{classBrokerInfoEx}

}




\newpage
\section{Known Problems and Caveats}
\label{caveats}
\input{caveats}


\begin{thebibliography}1
\bibitem[R1]{WMS} G.Avellino at al., \emph{The DataGrid Workload Management System: Challenges and Results}, Journal of Grid Computing, ISSN: 1570-7873, 2005, accepted.
\bibitem[R2]{jdl}\emph{JDL Attributes Specification}, EGEE-JRA1-TEC-555796-JDL-Attributes-v0-6 , \\ \url{https://edms.cern.ch/file/555796/1/}.
\bibitem[R3]{lb}\emph{LB Service User's Guide}, EGEE-JRA1-TEC-571273 , \\ \url{https://edms.cern.ch/file/571273/1/LB-guide.pdf}.
\bibitem[R4]{voms-core}\emph{VOMS User's Guide}, EGEE-JRA1-TEC-571991 , \\ \url{https://edms.cern.ch/file/571991/1/voms-guide.pdf}.
\bibitem[R5]{brokerinfo}\emph{The Resource Broker Info file}, Brokerinfo-access Guide , \\ \url{http://egee-jra1-wm.mi.infn.it/egee-jra1-wm/brokerinfo-access.shtml}.
\bibitem[R6]{jdl-lang}\emph{About Job Description Language}, About JDL , \\ \url{http://trinity.datamat.it/projects/EGEE/wiki/wiki.php?n=JDL.AboutJDL}.
\bibitem[R7]{jra1-arch}\emph{EGEE Middleware Architecture}, DJRA1.1 , \\ \url{https://edms.cern.ch/document/476451/1.0}.
\bibitem[R8]{jra1-design}\emph{Design of the EGEE gLite middleware external interfaces}, DJRA1.2 , \\ \url{https://edms.cern.ch/document/487871/1.0}.
\bibitem[R9]{jra3-arch}\emph{Global Security Architecture}, DJRA1.3 , \\ \url{https://edms.cern.ch/document/487004/1.1}.
\bibitem[R10]{jra1-arch2}\emph{EGEE Middleware Architecture (Review)}, EGEE-DJRA1.1-594698-v1.0 , \\ \url{https://edms.cern.ch/document/594698/1.0}.
\bibitem[R11]{jra1-design2}\emph{Design of the EGEE Middleware Grid Services (Review)}, EGEE-DJRA1.5-606574-v1.0 , \\ \url{https://edms.cern.ch/document/606574/1.0}.
\bibitem[R12]{WMPROXY}\emph{WMProxy User's Guide}, EGEE-JRA1-TEC-674643 , \\ \url{https://edms.cern.ch/document/674643/1}.
\end{thebibliography}

\clearpage

%\appendix



\end{document}
